Final Report

### 2022-05-09 Final Report.Rmd
second decade continent graphs

This shows the second decade 2007-2017.
```{r, echo=FALSE}
#High Population Deaths 2007-2017
p_high_second <- all_high_second %>%
  group_by(country) %>% 
  ggplot(aes(x= High_Deaths_07, y= High_Deaths_12, color= High_Deaths_17)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_point() +
  facet_wrap(~country)

interact_high_second<- p_high_second + labs(title="High Populated Countries", x="2007 Deaths", y="2012 Deaths")

ggplotly(interact_high_second)

#Low Population Deaths 2007-2017
p_low_second <- all_low_second %>%
  group_by(country) %>% 
  ggplot(aes(x= Low_Deaths_07, y= Low_Deaths_12, color= Low_Deaths_17)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_point() +
  facet_wrap(~country)

interact_low_second<- p_low_second + labs(title="Low Populated Countries", x="2007 Deaths", y="2012 Deaths")

ggplotly(interact_low_second)

>>>>

This shows the second decade 2007-2017.
```{r, echo=FALSE}
#High Population Deaths 2007
p_high_second_07 <- all_high_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_07, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_second_07<- p_high_second_07 + labs(title="High Populated Countries", x="2007 Deaths")

ggplotly(interact_high_second_07)

#High Population Deaths 2012
p_high_second_12 <- all_high_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_12, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_second_12<- p_high_second_12 + labs(title="High Populated Countries", x="2012 Deaths")

ggplotly(interact_high_second_12)

#High Population Deaths 2017
p_high_second_17 <- all_high_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= High_Deaths_17, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position = 'dodge')

interact_high_second_17<- p_high_second_17 + labs(title="High Populated Countries", x="2017 Deaths")

ggplotly(interact_high_second_17)

#Low Population Deaths 2007
p_low_second_07 <- all_low_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_07, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position='dodge')

interact_low_second_07<- p_low_second_07 + labs(title="Low Populated Countries", x="2007 Deaths")

ggplotly(interact_low_second_07)

#Low Population Deaths 2012
p_low_second_12 <- all_low_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_12, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position='dodge')

interact_low_second_12<- p_low_second_12 + labs(title="Low Populated Countries", x="2012 Deaths")

ggplotly(interact_low_second_12)

#Low Population Deaths 2017
p_low_second_17 <- all_low_second %>%
  group_by(country) %>% 
  ggplot(aes(x= country, y= Low_Deaths_17, fill=country)) +
  scale_color_gradient2(low = "light pink", mid = "pink", high = "dark violet", aesthetics = "color") +
  geom_col(position='dodge')

interact_low_second_17<- p_low_second_17 + labs(title="Low Populated Countries", x="2017 Deaths")

ggplotly(interact_low_second_17)
